Report: Illustration Results

### 2023-02-17 sections/01DataDescription.Rmd
:construction: figure folder fix

# Global Chunk Options
knitr::opts_chunk$set(
  fig.width = 12,
  fig.height = 8,
  fig.path = "../Figures/",
  include = FALSE,
  warning = FALSE,
  message = FALSE
)
```

>>>>

# Global Chunk Options
knitr::opts_chunk$set(
  fig.width = 12,
  fig.height = 8,
  fig.path = "../figures/",
  include = FALSE,
  warning = FALSE,
  message = FALSE
)
```
